---
title: "Control Chart Review - LACT02"
output: word_document
date: "15 January 2015"
---

```{r, echo=FALSE,message=FALSE}
data.raw <- read.csv("C:/Users/lkennedy/Dropbox/SRM Results review/SRM_data.csv", as.is=TRUE, header=TRUE)
colnames(data.raw)[1] <- "SAMPLE_NUMBER"
library(dplyr)
library(psych)
library(ggplot2)

Name <- data.raw$REPORTED_NAME[1]
Units <- tolower(sub("_P_","/",(data.raw$REPORTED_UNITS[1])))
testname <- substr(data.raw$ANALYSIS[1],1,6)
paste("Test Code :", testname)
```

The recent control samples with this test have been:

```{r, echo=FALSE, warning=FALSE, message=FALSE}

# Clean the data
data.in <- select(data.raw, everything())%>%
        arrange(SAMPLE_NUMBER)%>%
        select(ASSIGNED_OPERATOR, SAMPLING_POINT, ENTRY)%>%
        mutate(ENTRY = as.numeric(as.character(ENTRY)))%>%
        na.omit


boxplot(data.in$ENTRY~data.in$SAMPLING_POINT,
         main = paste("Comparative ",testname," SRM/IRM Results (Last 12 months)"),
        ylab = paste(Name," ", Units))
```

The most recent control chart (minus any outliers (shown in red) is:

```{r, echo=FALSE,message=FALSE}
j <- length(unique(data.in$SAMPLING_POINT))

remove.outliers <- function(x, na.rm = TRUE, ...) {
        qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
        H <- 1.5 * IQR(x, na.rm = na.rm)
        y <- x
        y[x < (qnt[1] - H)] <- NA
        y[x > (qnt[2] + H)] <- NA
        y
}
srm1 <- unique(data.in[2])

srm <- srm1[j,]

data.in3 <- data.in[data.in$SAMPLING_POINT==srm,]
names(data.in3) <- c("Operator", "SRM","A")

clean <- remove.outliers(data.in3$A)
xx <- describe(clean)

UCL <- xx$mean + 3*xx$sd
UWL <- xx$mean + 2*xx$sd
Centre <- xx$mean 
LWL <- xx$mean - 2*xx$sd
LCL <- xx$mean - 3*xx$sd
MU <- 2*xx$sd

CC <- c(UCL, UWL, Centre, LWL, LCL ,MU)
Labels <- c("UCL", "UWL", "Centre", "LWL", "LCL", "MU +/-")
Clines <- cbind(Labels, round(CC,3))
Clines <- as.data.frame(Clines)

plot(data.in3$A, 
        type="p", 
        pch= 19, 
        cex=1.0, 
        col ="red", 
        ylim = c(LCL*0.9,UCL*1.1),
        ylab = paste(Name," ", Units),
        xlab="")

par(new=T)

plot(clean, 
        type="o", 
        pch=19, 
        cex=1.0, 
        col="grey40", 
        ylim = c(LCL*0.9,UCL*1.1), 
        ylab = paste(Name," ", Units), 
        main = paste(srm, "(", Name,") Control Chart"),
        xlab="")

abline(h=Centre, col = "blue", lty=2, lwd=2)
abline(h=UCL, col = "red", lty=2, lwd=2)
abline(h=UWL, col = "darkgreen", lty=3, lwd=2)
abline(h=LWL, col = "darkgreen", lty=3, lwd=2)
abline(h=LCL, col = "red", lty=2, lwd=2)

```

The histogram of the data points is:

```{r, echo=FALSE}
hist(clean, breaks=20, xlab=srm,
     main = paste("Control Chart",srm,"data distribution"))
```

**Review**
1. Is it skewed?
2. Is it normal shaped?
.

The general statistics for the data are:

```{r,echo=FALSE}
print(describe(clean))
```

The values for the control lines used  in the chart are:

```{r, echo=FALSE}
print (Clines)
```

The results obtained by each operator are:

```{r, echo=FALSE}
boxplot(data.in3$A~data.in3$Operator, las=2)
```

Number of control samples run by each operator:

```{r, echo=FALSE}
table(data.in3$Operator)
```



